\textbf{COMP0078 Assignment 2}

### 2022-12-09 submission.tex
update figures and lin reg classifier
challenge question completed

\begin{document}
    \maketitle
\section{PART I}
\subsection{Kernel Perceptron}
\newpage
\section{PART II}
\subsection{Semi-supervised Learning via Laplacian Interpolation}

@@

\section{PART III}
\subsection{Questions}
\begin{itemize}
    \item[a.]
    \item[b.]
    \item[c.]
    \item[D.]\\
    We note that since for any $X_{t}$, $y_{t} = X_{1,t}$, we have the following
     expression representing the linear separability of our dataset:\\
    \[(v \cdot x_{t})y_{t} \ge 1\]\\
    Where $v = (1,0, \dots, 0)^{T}$. Note that $\|v\| =1$.\\
    Hence, in our online mistake bound for the perceptron, we have that $\gamma =1$.
    Further note that $\forall t$, $x_{t} \in {-1,1}^{n} \implies \|x_{t}\|^{2}
    = n$. This gives us that $R = max_{t} \|x_{t}\| = \sqrt{n}$.
    Hence our mistake bound for the perceptron algorithm is given by:\\

@@

\end{itemize}
\end{document}

>>>>

\begin{document}
    \maketitle
\section{PART I}
\subsection{Kernel Perceptron}
\subsubsection{Experimental Results}

\begin{itemize}
    \item[1.] Basic Results:

    \includegraphics{outputs/part1/q1.png}

    \item[2.] Cross Validation Results:

    \includegraphics{outputs/part1/q2.png}

    \item[3.] Confusion Matrix:

    \includegraphics{outputs/part1/q3_confusion.png}
\newpage
    \item[4.] Hardest to predict images:

    \includegraphics{outputs/part1/q4.png}
    \newpage
    \item[5.] Basic Results:

    \includegraphics{outputs/part1/q5_1.png}

    Cross Validation Results:

    \includegraphics{outputs/part1/q5_2.png}
\end{itemize}
\subsubsection{Discussions}
    Choice of Parameters that weren't cross validated

    Generalisation to k-classifiers

    Kernel Comparison

    Kernel Perceptron Implementation

\newpage
\section{PART II}
\subsection{Semi-supervised Learning via Laplacian Interpolation}

@@

\section{PART III}
\subsection{Questions}
\begin{itemize}
    \item[a.]
    \item[b.]
    \item[c.]
    \item[D.]\\
    We note that since for any $X_{t}$ , $y_{t} = X_{1,t}$ , we have the following
     expression representing the linear separability of our dataset:\\
    \[(v \cdot x_{t})y_{t} \ge 1\]\\
    Where $v = (1,0, \dots, 0)^{T}$. Note that $\|v\| =1$.\\
    Hence, in our online mistake bound for the perceptron, we have that $\gamma =1$.
    Further note that $\forall t$, $x_{t} \in {-1,1}^{n} \implies \|x_{t}\|^{2}
    = n$. This gives us that $R = max_{t} \|x_{t}\| = \sqrt{n}$.
    Hence our mistake bound for the perceptron algorithm is given by:\\

@@

     \item[E.]\\
     From our experimental observations we may expect the sample complexity of 1-NN
     to be lower bounded by some exponential function. We formalise this in the
     following proposition:\\

    \textbf{Proposition:}\\

    Following the data-generating distribution described above, we have that our sample complexity given by:\\

    $m(n) = \Omega (n)$ \\
    \textbf{Proof:}\\

    Suppose we sample a training set $S = \{(x_{1},y_{1}), \dots, (x_{n},y_{n})\} $ uniformly from the set $\{-1,1\}^{n}$, with associated labels
    defined by the rule $y | x = x_{1}$, and use this training set for inference on an
     arbitrary test point $(x,x_{1})$, sampled uniformly from the same set.
    \\
    We note the following observation:\\

    \textbf{Obs:}\\
    if $x \in S$, then $\mathcal{A}_{S}(x)) = y$, where y is the true label for x. \\

    To justify this, observe that our dataset represents a realiseable learning problem,
    and as such, if $(x,y), (x \prime,y \prime)$ are datapoints sampled from our distribution,
    $x = x \prime \implies y = y \prime $. Trivially, x is the 1-nearest neighbour to itself,
    so the algorithm makes a correct prediction for any datapoint present in our training set.\\

    Hence, $\mathcal{A}_{S}$ makes an error on x $\implies x \notin S$.

    Hence, the set of all training sets that make an error on x is contained in the set of all
    training sets not containing x. \\

    Hence, for a given x, $P_{S}(\mathcal{A}_{S}(x) \ne y) \le P_{S}(x \notin S)$.\\

    Since S is a collection of points sampled iid from our data generating distribution, \\
    $P_{S}(x \notin S) = \prod_{i=1}^{m}P(x_{i} \ne x) = \prod_{i}(1 - P(x_{i} = x)) = (1 - 2^{-n})^{m}$\\

    We note that our choice of x was arbitrary, and since we sampled x uniformly, we arrive at the 
    following generalisation error bound:\\

    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le (1 - 2^{-n})^{m} $\\
    Using the identity $1-x \le e^{-x}$ provided frequently in the notes, we simplify this bound to give:
    \\
    \\

    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m)$
    \\
    Suppose we seek m such that our generalisation error is less than some fixed $\epsilon$. \\
    \\
    Hence we require $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m) \le \epsilon$\\
    \\
    $\implies -m2^{-n} \le log(\epsilon)$\\

    Hence, $m \ge -log(\epsilon)2^{n} = log(\frac{1}{\epsilon}) 2^{n}$\\

    $\implies m = \Omega(2^{n})$\\
    $\square$
\end{itemize}
\end{document}
